Final Project Code

### 2022-12-12 Project_Final_Code.Rmd
Fixed GAM

---
title: "Final Project Code ALL"
author: "Emily, Julian, Jacob, and Aristo"
date: '2022-11-20'
output: 
  html_document:
    df_print: paged
    toc: true
    code_download: true
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

@@

gam1_output %>%
    rmse(truth = Gross, estimate = .pred)

gam1_output %>%
    rsq(truth = Gross, estimate = .pred)
```

@@

# Visualize Residuals
gam1_output <- new_mod %>%
    predict(new_data = imdb_clean) %>%
    bind_cols(imdb_clean) %>%
    mutate(resid = Gross - .pred)

ggplot(gam1_output, aes(x = .pred, y = resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, color = "red") + 
    labs(x = "Prediction",
         y = "Residuals", 
         title = "Residuals vs. Predictions") +
    theme_classic()

ggplot(gam1_output, aes(x = Runtime, y = resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, color = "red")  + 
    labs(x = "Runtime",
         y = "Residuals", 
         title = "Residuals vs. Runtime") +
    theme_classic()

ggplot(gam1_output, aes(x = IMDB_Rating, y = resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, color = "red")  + 
    labs(x = "IMDB Rating",
         y = "Residuals", 
         title = "Residuals vs. IMDB Rating") +
    theme_classic()

ggplot(gam1_output, aes(x = No_of_Votes, y = resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, color = "red")  + 
    labs(x = "Number of Votes",
         y = "Residuals", 
         title = "Residuals vs. Number of Votes") +
    theme_classic()
```

@@

```{r}
gam1_output %>%
    rmse(truth = Gross, estimate = .pred) #GAM
```

>>>>

---
title: "Final Project Code"
author: "Emily, Julian, Jacob, and Aristo"
date: '2022-11-20'
output: 
  html_document:
    df_print: paged
    toc: true
    code_download: true
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE, tidy = TRUE)
```

@@

gam1_output %>%
    rmse(truth = Gross, estimate = .pred)
```

@@

# Visualize Residuals
cv_output_spline2 <- new_mod %>%
    predict(new_data = imdb_clean) %>%
    bind_cols(imdb_clean) %>%
    mutate(resid = Gross - .pred)

ggplot(cv_output_spline2, aes(x = .pred, y = resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, color = "red") + 
    labs(x = "Prediction",
         y = "Residuals", 
         title = "Residuals vs. Predictions") +
    theme_classic()

ggplot(cv_output_spline2, aes(x = Runtime, y = resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, color = "red")  + 
    labs(x = "Runtime",
         y = "Residuals", 
         title = "Residuals vs. Runtime") +
    theme_classic()

ggplot(cv_output_spline2, aes(x = IMDB_Rating, y = resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, color = "red")  + 
    labs(x = "IMDB Rating",
         y = "Residuals", 
         title = "Residuals vs. IMDB Rating") +
    theme_classic()

ggplot(cv_output_spline2, aes(x = No_of_Votes, y = resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, color = "red")  + 
    labs(x = "Number of Votes",
         y = "Residuals", 
         title = "Residuals vs. Number of Votes") +
    theme_classic()
```

@@

```{r}
cv_output_spline2 %>%
    rmse(truth = Gross, estimate = .pred) #GAM
```
